### 2024-10-03 esop25/metalang.tex
checkpoint

We define a big-step evaluation relation $\redx$ in Figures
\ref{fig-metaprotexprsemantics} and \ref{fig-metaprotinstrsemantics}
for expressions and instructions, respectively.  In this definition we
write $e[\mv/y]$ and $\instr[\mv/y]$ to denote the substitution of
$\mv$ for free occurrences of $y$ in $e$ or $\instr$ respectively. The
rules are mostly standard. Note that we do not include an evaluation
rule for the form $\eqcast{\mx{e}{e}}{\notg{\phi}}$ which only has
relevance for the type system and which we assume is erased from
programs prior to evaluation. We defer discussion of this form,
as well as the syntactic category $\notg{\phi}$, to the next
Section.

@@

\begin{mathpar}
  \inferrule[Mesg]
            {e_1 \redx x \\ e_2 \redx \be \\ e_3 \redx \cid \\ \atj{\toeq{\elab{\be}{\cid}}}{R_2}{\ty} \\
              \itj{\cid}{\be}{V}}
            {\mtj{\xassign{e_1}{e_2}{e_3}}{\eqs}{(x:\ty)}{R_1;R_2}{(x : \ity{\cid}{V})}{\eqs \wedge x \eop \toeq{\elab{\be}{\cid}}}}

  \inferrule[Encode]
            {e_1 \redx w \\ e_2 \redx \cid \\ \notg{\phi} \redx \phi \\
              \eqs \models \toeq{\elab{\be}{\cid}} \eop \phi\\
              \atj{\phi}{R}{\ty}}
            {\mtj{\eqcast{\mx{e_1}{e_2}}{\notg{\phi}}}{\eqs}{(\mx{w}{\cid}:\ty)}{R}{\varnothing}{\eqs}}

  \inferrule[App]
            {\tsig(f) = \dht{y_1,\ldots,y_n}{\notg{\eqs_1}}{\notg{\Gamma}}{\notg{R}}{\notg{\Delta}}{\notg{\eqs_2}} \\
              e_1 \redx \mv_1\ \cdots\ e_n \redx \mv_n \\
              \subn = [\mv_1/y_1]\cdots[\mv_n/y_n] \\
              \subn(\hty{\notg{\eqs_1}}{\notg{\Gamma}}{\notg{R}}{\notg{\Delta}}{\notg{\eqs_2}}) \redx
                    \hty{\eqs_1}{\Gamma}{R}{\Delta}{\eqs_2} \\
              \eqs \models \eqs_1}
            {\mtj{f(e_1,\ldots,e_n)}{\eqs}{\Gamma}{R}{\Delta}{\eqs \wedge \eqs_2}}

  \inferrule[Seq]          
            {\mtj{\prog_1}{\eqs_1}{\Gamma_1}{R_1}{\Delta_1}{\eqs_2} \\
             \mtj{\prog_2}{\eqs_2}{\Gamma_2}{R_2}{\Delta_2}{\eqs_3}}
            {\mtj{\prog_1;\prog_2}{\eqs_1}{\Gamma_1;\Gamma_2}{R_1;R_2}{\Delta_1;\Delta_2}{\eqs_3}}
\end{mathpar}

\begin{mathpar}
  \inferrule[Sig]
            {\codebase(f) = y_1,\ldots,y_n, \instr \\
              \subn = [\mv_1/y_1]\cdots[\mv_n/y_n] \\
              \subn(\hty{\notg{\eqs_1}}{\notg{\Gamma}}{\notg{R}}{\notg{\Delta}}{\notg{\eqs_2}}) \redx
                    \hty{\eqs_1}{\Gamma}{R}{\Delta}{\eqs_2} \\
              \mtj{\subn(\instr)}{\eqs_1}{\Gamma}{R}{\Delta}{\eqs} \\
              \eqs \models \eqs_2}
            {f : \dht{y_1,\ldots,y_n}{\notg{\eqs_1}}{\notg{\Gamma}}{\notg{R}}{\notg{\Delta}}{\notg{\eqs_2}}}
\end{mathpar}

>>>>

We define a big-step evaluation relation $\redx$ in Figures
\ref{fig-metaprotexprsemantics} and \ref{fig-metaprotinstrsemantics}
for expressions and instructions, respectively.  In this definition we
write $e[\mv/y]$ and $\instr[\mv/y]$ to denote the substitution of
$\mv$ for free occurrences of $y$ in $e$ or $\instr$ respectively. The
rules are mostly standard. Note that we do not include an evaluation
rule for the form $\eqcast{\mx{e}{e}}{\notg{\phi}}$ which is a type
annotation that we assume is erased from programs prior to
evaluation. We defer discussion of this form, as well as the syntactic
category $\notg{\phi}$, to the next Section.

@@

\mtjfig
